Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-07 tex/VHzQ.tex
color_color/W1W2_plots/ update
VHzQ.tex update

@@

We thank Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA), and 
also the VISTA Science Archive (VSA). We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.

We thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.

We thank Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion.

>>>>

The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154 
(see Figure~\ref{fig:DELS_J1048}).

@@

We thank:
\begin{list}{$\circ$}{}  
\item Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA) and the VISTA Science Archive (VSA). 
\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
\end{list}
